---
title: "Introduction to FARS Package"
author: "Christopher Hughes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Here is a short introduction to the FARS package. We'll walk you through:

- What FARS data is
- Why we want to work with the data
- Each of the functions in the package

## The FARS data

The functions in this package are for use with the data from the US National Highway Traffic Safety Administration's ([via](http://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS))) Fatality Analysis Reporting System. This is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

## Functions

### Read Fars files

fars_read function allows you to read in file from your directory.

#### Example

```{r}

library(Fars)

data <- fars_read("accident_2014.csv.bz2")
head(data)

```

### Make filename

make_filename function allows you to create suitable filenames for a given year.

#### Example

```{r}
data <- make_filename(2014)
data
```

### Read Dates in files

fars_read_years is a function that will read the data files and return a tibble containing the months and years of all of the records.

#### Example

```{r}
list.files()
data <- fars_read_years(2014)

head(data)
```
